
---
output: # rmarkdown::github_document
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 3.  Working with Data Frame. Base R Style"
---

Problems and Solutions
-------
-------

1. Create the following data frame

| Rank 	| Age 	| Name  	|
|:------	|:-----	|:-------	|
| 0    	| 28  	| Tom   	|
| 1    	| 34  	| Jack  	|
| 2    	| 29  	| Steve 	|
| 3    	| 42  	| Ricky 	|

```{r}
df1 = data.frame(Rank = c(0,1,2,3),
                Age = c(28,34,29,42),
                Name = c('Tom', 'Jack', 'Steve','Ricky'))

df1
```

2. Use `read.csv` to import the Covid19 Vaccination data from WHO: [link](https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv).

```{r}
df2 = read.csv("https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv")

head(df2)
```

2. Show the names of the variables in the data

```{r}
names(df2)
```

3. How many columns and rows the data have? 

```{r}
str(df2)
```

4. How many missing values are there?  Show the missing values by columns.  What variable has the most number of missing values?

```{r}
sum(is.na(df2))

colSums(is.na(df2))
```

There are no missing values in this dataset

5. What is the class of the `date` column. Change the `date` columns to `date` type using the `as.Date` function. Show the new class of the `date` column. 

```{r}
class(df2$date)

df2$date = as.Date(df2$date)

class(df2$date)
```

6. Capitalize the names of all the variables

```{r}
names(df2)[1] = "Date"
names(df2)[2] = "State"
names(df2)[3] = "Fips"
names(df2)[4] = "Cases"
names(df2)[5] = "Deaths"

names(df2)
```

7. Find the average number of cases per day. Find the maximum cases a day.  

```{r}
mean(df2$Cases, na.rm=TRUE)

max(df2$Cases, na.rm=TRUE)
```

8. How many states are there in the data?  

```{r}
length(unique(df2$State))
```

9. Create a new variable `weekdays` to store the weekday for each rows. 

```{r}
df2$weekdays = weekdays(df2$Date)

table(df2$weekdays)
```

10. Create the categorical variable `death2` variable taking the values as follows

- `has_death` if there is a death that day
-  `no_death` if there is no death that day

Find the frequency and relative frequency of `no_death` and `has_death`.

```{r}
df2$death2 = ifelse(df2$Deaths==0,'no_death','has_death')

table(df2$death2)
```

11. Find the first quartile (Q1), second quartile (Q2) and and third quartile (Q3) of the variable `death`. (Hint:  Use the `summary` function)

```{r}
summary(df2$Deaths)
```

12. Create the categorical variable `death3` variable taking the values as follows

- `low_death` if the number of deaths smaller than the 25 percentile (Q1)

- `mid_death` if the number of deaths from Q1 to Q3

- `high_death` if the number of deaths greater than Q3

```{r}
library(tidyverse)
df2$death3 = case_when(df2$Deaths < 842 ~ "low_death",
                             df2$Deaths < 12703 ~ "mid_death",
                             TRUE ~ "high_death")

table(df2$death3)
```

13. Find the average cases in Rhode Island in 2021

```{r}
df3 = df2[(df2$State=="Rhode Island")&(df2$Date>="2021-01-01")&
            (df2$Date<"2022-01-01"),]

mean(df3$Cases)
```

14. Find the median cases by weekdays in Rhode Island in 2021 

```{r}
by(df3$Cases,df3$weekdays,median)
```

15. Compare the median cases in Rhode Island in June, July, August and September in 2021. 

```{r}
df4 = df2[(df2$State=="Rhode Island")&(df2$Date>="2021-06-01")&
            (df2$Date<"2021-10-01"),]
df4$Month = substr(df4$Date,6,7)

by(df4$Cases,df4$Month,median)
```

16.  Find your own dataset, import it and implement the following functions on the data

- head
- str
- names
- mean, min, max
- table
- is.na
- colSums
- class
- cor
- by
- ifelse
- case_when

```{r}
adult_census = read.csv("C:/Users/student/OneDrive - Bryant University/College/7th Semester/R/adult_census.csv")

head(adult_census)
str(adult_census)
names(adult_census)
mean(adult_census$age)
min(adult_census$age)
max(adult_census$age)
table(adult_census$age)
sum(is.na(adult_census))
colSums(is.na(adult_census))
class(adult_census)
cor(adult_census$education.num, adult_census$hours.per.week)
by(adult_census$hours.per.week, adult_census$education.num, mean)
head(ifelse(adult_census$education=="Doctorate", "Doctorate", "Less Than Doctorate"))
adult_census$education.level = case_when(adult_census$education.num <= 12 ~ "High School",
                             TRUE ~ "Higher Degree")
table(adult_census$education.level)
```

17.  In the dataset in #16, practice the follows.  You can reuse the code of 16. 

- Create a categorical variable from a continuous variable
- From one categorical variable, create a new categorical variable with fewer categories

If you do not have a data, you can use [the titanic dataset](https://www.kaggle.com/competitions/titanic/overview), which can be downloaded at [this link](../data/titanic.csv)

```{r}
adult_census$education.level = case_when(adult_census$education.num <= 12 ~ "High School",
                                         TRUE ~ "Higher Degree")
table(adult_census$education.level)

adult_census$education.level2 = case_when(adult_census$education == "Doctorate" ~ "Doctorate",
                                          TRUE ~ "Less Than Doctorate")
table(adult_census$education.level2)
```

