
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 7: Visualization - Some aspects of ggplot2"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment7.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

-------

Use the data of your own.  Produce the following types of plots and comment on each plot. Plots should be meaningful. If you use the data we used in class, make sure the plots are not the same as the ones in the slides. All plots should have title, caption, appropriate labels on x and y-axis. 

-------

```{r}
library(tidyverse)
df = read_csv("C:/Users/student/OneDrive - Bryant University/College/7th Semester/R/adult_census.csv")
library(ggplot2)
library(dplyr)
```

1. Make a plot using `facet_wrap` by one categorical variable (`facet_wrap(~variable1)`)

```{r}
df %>% ggplot() + geom_point(mapping=aes(x=age, y=hours.per.week)) + facet_wrap(~sex) +
  labs(x='Age', 
       y = 'Hours Per Week', 
       title = 'Hours Worked Per Week by Age and Sex', 
       caption = 'No apparent patterns but hours per week somewhat increase by age, and males generally work more hours than females.')
```

2. Make a plot using `facet_wrap` by two categorical variables (`facet_wrap(~variable1+variable2)`)

```{r}
df %>% ggplot() + geom_point(mapping=aes(x=age, y=hours.per.week)) + facet_wrap(~sex+income) +
  labs(x='Age', 
       y = 'Hours Per Week', 
       title = 'Hours Worked Per Week by Age, Sex, and Income', 
       caption = 'Hours per week generally increase by age and income, and males somewhat seem to work more hours than females.')
```

3. Make a plot using `position ='dodge'`.

```{r}
df %>% ggplot() + geom_bar(mapping=aes(x=sex, fill=income), position = 'dodge') +
  labs(x='Sex', 
       y='Count',
       fill = 'Income', 
       title = 'Count of Sex By Income Level', 
       caption = 'Many more males than females in data, but a much higher percentage of males earn >50K than for females.')
```

4. Make a plot using `position ='fill'`. 

```{r}
df %>% ggplot() + geom_bar(mapping=aes(x=sex, fill=income), position = 'fill') +
  labs(x='Sex', 
       y='Percent',
       fill = 'Income', 
       title = 'Percent of Sex Per Income Level', 
       caption = 'A much higher percentage of males earn >50K than for females.')
```

5. Make a plot using `geom_col`.

```{r}
df %>% group_by(income) %>% summarise(average_age=mean(age, na.rm=TRUE)) %>% 
  ggplot() + geom_col(mapping=aes(x=income, y=average_age)) + 
  labs(x='Income', 
       y='Average Age',
       title = 'Average Age Per Income Level', 
       caption = 'The average age increases as income level increases.')
```

6. Change the theme of one of your plots. 

```{r}
df %>% ggplot() + geom_bar(mapping=aes(x=sex, fill=income), position = 'fill') + theme_dark() +
  labs(x='Sex', 
       y='Percent',
       fill = 'Income', 
       title = 'Percent of Sex Per Income Level - Dark Theme', 
       caption = 'A much higher percentage of males earn >50K than for females.')
```

7. Make a plot using combo filter + ggplot

```{r}
df %>% filter(age>=30, age<=50) %>% ggplot() + geom_bar(mapping=aes(x=sex, fill=income)) +
  labs(x='Sex', 
       y='Count',
       fill = 'Income', 
       title = 'Count of Sex By Income Level for Ages 30-50', 
       caption = 'Many more males than females in data, but a much higher percentage of males earn >50K than for females.')
```

8. Make a plot using combo group_by + summarise + geom_col

```{r}
gg = df %>% group_by(sex,age) %>% summarise(mean_education = mean(education.num)) %>% ggplot() +
  geom_col(aes(x=age, y=mean_education, fill=sex), position = 'dodge') +
  labs(x='Age', 
       y='Average Education Level',
       fill = 'Sex', 
       title = 'Average Education Level by Age and Sex', 
       caption = 'Females generally have a higher average education level per age until around age 35 when it changes to males usually having the higher level per age.')
ggsave(filename = 'Question9.png', plot = gg)
gg
```

9. Save a plot and put a link of the plot to your Github Webpage.  To link a plot `abc.png` you just need to insert the following on the README.md

```{r, eval=FALSE}
[Assignment 7, Question 8 Plot](Question8.png)
```

10. In this question, we will use  the Covid19 vaccination data for the US. The data and data dictionary can be found at the below link:

- [Data](https://raw.githubusercontent.com/owid/covid-19-data/master/public/data/vaccinations/vaccinations-by-manufacturer.csv)

```{r}
library(tidyverse)
df <- read_csv('https://raw.githubusercontent.com/owid/covid-19-data/master/public/data/vaccinations/vaccinations-by-manufacturer.csv')
```

`Geom_point` makes scatter plots, which plot two numeric (or Date) variables. A third categorical variable is often brought in for color. For example, we can compare different vaccine types used in the US by

```{r}
df %>% 
  filter(location=='United States') %>% 
  ggplot()+
  geom_point(mapping = aes(x = date, y = total_vaccinations, color = vaccine))
```

Do the follows. 

  - Use `geom_point` to compare the vaccines used by date in Argentina in 2022. 

```{r}
df$date = as.Date(df$date)

df %>% filter(location=='Argentina', date>="2022-01-01") %>% ggplot() + 
  geom_point(mapping = aes(x = date, y = total_vaccinations, color = vaccine)) +
  labs(x='Date', 
       y='Total Vaccinations',
       color = 'Vaccine', 
       title = 'Total Vaccines Used by Date in Argentina 2022', 
       caption = 'Sinopharm and Oxford are the most used vaccines, but Pfizer and Moderna rose greatly over time.')
```

  - Change `geom_point` to `geom_line` in the above codes to have the corresponding line plots. 

```{r}
df %>% filter(location=='Argentina', date>="2022-01-01") %>% ggplot() + 
  geom_line(mapping = aes(x = date, y = total_vaccinations, color = vaccine)) +
  labs(x='Date', 
       y='Total Vaccinations',
       color = 'Vaccine', 
       title = 'Total Vaccines Used by Date in Argentina 2022', 
       caption = 'Sinopharm and Oxford are the most used vaccines, but Pfizer and Moderna rose greatly over time.')
```

11. (Using the same dataset as in 10.) Sometime we need to do some calculations on the data before plotting. For example, the below codes is to compare the total vaccines (including all types of vaccines) by date between the US and the EU

```{r}
# the total vaccines (including all types of vaccines) by date
d1 <- df %>% 
  filter(location %in% c('United States', 'European Union')) %>% 
  group_by(date, location) %>% 
  summarise(total_vac2=sum(total_vaccinations, na.rm=TRUE))

# Plot
d1 %>% ggplot() + geom_point(mapping=aes(x=date, y=total_vac2, color=location))
```

Notice that the above codes could be piped in one 

```{r, eval=FALSE}
df %>% filter(location %in% c('United States', 'European Union')) %>% 
  group_by(date, location) %>% summarise(total_vac2=sum(total_vaccinations, na.rm=TRUE)) %>% 
  ggplot() + geom_point(mapping=aes(x=date, y=total_vac2, color=location))
```

Do the follows. 

- Use `geom_point` compare the total vaccines (including all types of vaccines) by date between countries/regions in Asia

```{r}
df %>% filter(location %in% c('Cyprus', 'Hong Kong', 'Japan', 'Nepal', 'South Korea')) %>% 
  group_by(date, location) %>% summarise(total_vac2=sum(total_vaccinations, na.rm=TRUE)) %>% 
  ggplot() + geom_point(mapping=aes(x=date, y=total_vac2, color=location)) +
  labs(x='Date', 
       y='Total Vaccinations',
       color = 'Location', 
       title = 'Total Vaccines Used by Date in Asian Regions', 
       caption = 'Japan quickly rose to have the highest total vaccinations over time by a wide margin.')
```

- Use `geom_point` compare the total vaccines (including all types of vaccines) by date between countries/regions in South America in 2021

```{r}
df %>% filter(location %in% c('Argentina', 'Chile', 'Ecuador', 'Peru'), date>="2021-01-01",
              date<"2022-01-01") %>% group_by(date, location) %>% 
  summarise(total_vac2=sum(total_vaccinations, na.rm=TRUE)) %>% 
  ggplot() + geom_point(mapping=aes(x=date, y=total_vac2, color=location)) +
  labs(x='Date', 
       y='Total Vaccinations',
       color = 'Location', 
       title = 'Total Vaccines Used by Date in South American Countries', 
       caption = 'Argentina quickly rose to have the highest total vaccinations over time by a wide margin.')
```

