
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 7 - Extra Credits: Practice dplyr and ggplot2"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment7_extra_credits.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas



```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```


-------

1. Import the data at https://bryantstats.github.io/math421/data/ds_salaries.csv

    The data description can be found at https://www.kaggle.com/datasets/saurabhshahane/data-science-jobs-salaries

```{r}
library(tidyverse)
df = read_csv("https://bryantstats.github.io/math421/data/ds_salaries.csv")
library(ggplot2)
library(dplyr)
```

2. Is there any column that contains NAs?

```{r}
colSums(is.na(df))
```
No columns contain NA

3. What are the most frequent job titles in the data?  

```{r}
table(df$job_title)
```
The most frequent jobs are Data Scientist, Data Engineer, and Data Analyst, respectively

4. Find the average salary data of the three most frequent job titles in the data. 

```{r}
df %>% filter(job_title=="Data Scientist"|job_title=="Data Engineer"|job_title=="Data Analyst") %>% group_by(job_title) %>% summarise(average_salary = mean(salary_in_usd))
```

5. What is the job title that has the highest average salary?

```{r}
df %>% group_by(job_title) %>% summarise(average_salary = mean(salary_in_usd)) %>% 
  arrange(-average_salary)
```
Data Analytics Lead

6. Which country gives the highest salary on average? 

```{r}
df %>% group_by(employee_residence) %>% summarise(average_salary = mean(salary_in_usd)) %>% 
  arrange(-average_salary)
```
Malaysia

7. Plot five meaningful plots. All plots should have title, caption, and appropriate labels.

```{r}
df %>% ggplot() + geom_point(mapping=aes(x=experience_level, y=salary_in_usd)) +
  labs(x='Experience Level', 
       y = 'Salary', 
       title = 'Salary By Experience Level', 
       caption = 'EX and SE experience levels appear to generally result in higher salaries than EN and MI.')

df %>% ggplot() + geom_bar(mapping=aes(x=remote_ratio, fill=experience_level), position = 'dodge') +
    labs(x='Remote Ratio', 
         y='Count',
         fill = 'Experience Level', 
         title = 'Count By Experience Level For Different Remote Ratios', 
         caption = 'All experience levels have their largest proportion working for companies 
         with a 100% remote ratio, likely because the remoteness has become preferred.')

df %>% group_by(employment_type) %>% summarise(average_salary=mean(salary_in_usd)) %>% 
  ggplot() + geom_col(mapping=aes(x=employment_type, y=average_salary)) + 
  labs(x='Employment Type', 
       y='Average Salary',
       title = 'Average Salary Per Employment Type', 
       caption = 'The CT employment type has the highest average salary by far, while FL and PT types result in very low salaries on average.')

df %>% ggplot() + geom_point(mapping=aes(x=work_year, y=salary_in_usd)) + 
  facet_wrap(~remote_ratio) +
  labs(x='Year', 
       y = 'Salary', 
       title = 'Salary by Year and Remote Ratio', 
       caption = 'Generally, jobs with 100 remote ratios pay higher salaries, and salaries increased in 2021 and mostly decreased in 2022.')

df %>% ggplot() + geom_bar(mapping=aes(x=employment_type, fill=experience_level), position = 'dodge') +
    labs(x='Employment Type', 
         y='Count',
         fill = 'Experience Level', 
         title = 'Count By Experience Level For Different Employment Types', 
         caption = 'The majority of data is for FT employees, 
         with most of them having SE or MI experience levels, 
         while the other employment types do not even contain all 4 experience levels.')
```

