
---
output: # rmarkdown::github_document
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 4 - Data Wrangling with `dplyr`"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment4.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- Notice that if there is `eval=FALSE` in the first line of the code chunk, the chunk will not be execute.

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas under Assignment 4. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

-------

#### 1. Install `tidyverse` package

An R package can be installed by `install.packages` function. Install `tidyverse` if you have not done so. 

```{r, eval=FALSE}
install.packages('tidyverse')
```

-------

#### 2. Read the data using `read_csv`

Use `read_csv` function to import the US Covid 19 data at [link](https://covidtracking.com/data/download/all-states-history.csv).  Don't forget to import `tidyverse` (library(tidyverse)) so that you can use read_csv. 

```{r}
library(tidyverse)
df = read_csv("https://covidtracking.com/data/download/all-states-history.csv")
```

-------

#### 3.  Fix the date and ceate some new variables

`lubridate` is a package of the `tidyverse` packages.  We will make uses of `lubridate` in this question.

- Use the below codes to create `month`, `weekday` and `monthday` variables

```{r}
library(lubridate)
df$month = month(df$date)

# day of the week
df$weekday = wday(df$date)

# day of the month
df$monthday = mday(df$date)
```

-------

#### 4. Create new variables with `case_when`. 

The function `case_when` is a good option to create a new variable from existing variable.  For example, this below codes create a new variable, `daily_death`, from `deathIncrease` variable.  `deathIncrease` is the number of daily new death by Covid19.  The new variable `daily_death` takes three values:  low (if `deathIncrease` less than 3), medium (`deathIncrease` from 3 to 14), and high (`deathIncrease` more than 14).  Please notice that this can also be done in a different way as shown in Assignment 3. 

```{r, eval=FALSE}
df$daily_death = case_when(df$deathIncrease <3 ~ 'low',
                           df$deathIncrease <=14 ~ 'medium',
                           TRUE ~ 'high')
```

- Create variable `month2` that takes three values: early_month (day of the month from 1-10), mid_month (day of the month from 11-20), and end_month (day of the month > 20).

- Create variable `weekend` that takes two values:  1 if it's Saturday or Sunday or 0 otherwise. 

```{r}
df$month2 = case_when(df$monthday <= 10 ~ "early_month",
                      df$monthday <= 20 ~ "mid_month",
                      TRUE ~ "end_month")

df$weekend = case_when(df$weekday == 6 ~ 1,
                       df$weekday == 7 ~ 1,
                       TRUE ~ 0)
```

-------

#### 5. Select function

Use the select function to deselect the column `totalTestsViral` from the data.

```{r}
df %>% select(-totalTestsViral)
```

-------

#### 6. Pipe Operator ( %>% )

Pipe operator offers another way to write R codes. Many times, it makes the codes more readable.  Pipe works very well with all the `tidyverse` packages. Refer to [these slides](../slides/4_dplyr.html#15) (slide 15, 16, 17 and 18) to rewrite the below codes using pipe operator

```{r, eval=FALSE}
x = c(1:10)

# square root of x: sqrt(x)
x %>% sqrt

# sum(sqrt(x))
x %>% sqrt %>% sum

# log(sum(sqrt(x)))
x %>% sqrt %>% sum %>% log

# log base 2 of 16: log(16, 2)
16 %>% log2
```

-------

#### 7. Combo 1: group_by + summarise

This combo is used when you want to apply a function/calculation to different groups of the data. For example, to calculate the average number of cases (`positiveIncrease`) by `dataQualityGrade`, we use:

```{r, eval=FALSE}
df %>% group_by(weekday) %>% summarise(mean(positiveIncrease))
```

- Calculate the median number of cases (`positiveIncrease`) by `month`

- Calculate the average number of cases (`positiveIncrease`) by `month2`

- Calculate the median number of cases (`positiveIncrease`) by `weekend`

```{r}
df %>% group_by(month) %>% summarise(median(positiveIncrease))
df %>% group_by(month2) %>% summarise(mean(positiveIncrease))
df %>% group_by(weekend) %>% summarise(median(positiveIncrease))
```

-------

#### 8. Combo 2: filter + group_by + summarise

An example: to calculate the average number of cases (`positiveIncrease`) in January and February separately, we use:

```{r, eval=FALSE}
df %>% filter(month==1|month==2) %>% group_by(month) %>% 
  summarise(positive_increase = mean(positiveIncrease))
```

- Calculate the median number of cases (`positiveIncrease`) on the weekend by `month` in October and November 2020. 

- Calculate the average number of death at different periods of a month (`month2` variable) in Fall 2020

- Compare the average number of hospitalizations between weekdays and weekends in Summer 2020

```{r}
q8 = subset(df, month == 10 | month == 11,)
q8 %>% filter(month==10|month==11|weekend==1) %>% group_by(month) %>% 
  summarise(number_cases = median(positiveIncrease))

df %>% filter(month==9|month==10|month==11) %>% group_by(month2) %>% 
  summarise(number_death = mean(deathIncrease))

df %>% filter(month==6|month==7|month==8) %>% group_by(weekend) %>% 
  summarise(number_hospitalizations = mean(hospitalizedIncrease))
```

- Redo Questions 14 and 15 in [Assignment 3](assignment3.html) using the combos.  Notice:  you also need to use the data used in Assignment 3.  

14. Find the median cases by weekdays in Rhode Island in 2021 

```{r}
df2 = read_csv("https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv")
df2$date = as.Date(df2$date)
df2$weekdays = weekdays(df2$date)

df2 %>% filter(state=="Rhode Island"|date>="2021-01-01"|date<"2022-01-01") %>% 
  group_by(weekdays) %>% summarise(number_cases = median(cases))
```

15. Compare the median cases in Rhode Island in June, July, August and September in 2021.

```{r}
df2$month = substr(df2$date,6,7)
df3 = subset(df2, month == "06" | month == "07" | month == "08" | month == "09", select=c(date,state,fips,cases,deaths,month))

df3 %>% filter(state=="Rhode Island"|date>="2021-06-01"|date<"2021-10-01") %>% 
  group_by(month) %>% summarise(number_cases = median(cases))
```

-------

#### 9. Combo 3: filter + group_by + summarise + arrange

Use the arrange function to find a month that has the highest number of deaths on the weekend. 

```{r}
df %>% filter(weekend==1) %>% group_by(month) %>% 
  summarise(max_deaths = max(deathIncrease)) %>% arrange(-max_deaths)
```

-------

#### 10. Use your own dataset and implement the follows functions or combos. You can use the [Adult Census Income](../data/adult_census.csv) or [Titanic data](../data/titanic.csv). 

- select
- filter
- mutate
- summarise
- arrange
- count
- count + arrange
- filter + count + arrange
- group_by + summarise
- filter + group_by + summarise
- filter + group_by + summarise + arrange

```{r}
df4 = read_csv("C:/Users/student/OneDrive - Bryant University/College/7th Semester/R/adult_census.csv")

df4 %>% select(-race)
df4 %>% filter(education == "HS-grad")
df4 %>% mutate(total_gain = capital.gain - capital.loss)
df4 %>% summarise(mean_education = mean(education.num))
df4 %>% arrange(education.num)
df4 %>% count(education.num)
df4 %>% count(education.num) %>% arrange(-education.num)
df4 %>% filter(workclass == "Private") %>% count(education.num) %>% arrange(-education.num)
df4 %>% group_by(education.num) %>% summarise(min_hours = min(hours.per.week))
df4 %>% filter(workclass == "Private") %>% group_by(education.num) %>% 
  summarise(min_hours = min(hours.per.week))
df4 %>% filter(workclass == "Private") %>% group_by(education.num) %>% 
  summarise(min_hours = min(hours.per.week)) %>% arrange(-education.num)
```

