
---
output: # rmarkdown::github_document
  html_document:
    theme: cerulean
    toc: true
  pdf_document: default
  word_document: default
title: "Assignment 5: Handle Missing Values"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment5.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

-------

**The data:** 

This assignment works with the Adult Census Data that can be downloaded at [this link.](https://bryantstats.github.io/math421/data/adult_census_missing.csv)

-------

**Questions**

1. Use `read_csv` to import the data.  Show the number of NAs for each columns.   

```{r}
library(tidyverse)
df = read_csv("https://bryantstats.github.io/math421/data/adult_census_missing.csv")

colSums(is.na(df))
```

2. Using function `aggr` the VIM package to plot the number of NAs for each column. 

```{r}
library(VIM)
aggr(df)
```

3. Find other forms of missing values. Hint: You can use the `table` function to check if there are suspicious categories (Unknown, for example) in a variable. What are all other forms of missing values shown in the data?

```{r}
table(df$workclass)
table(df$education)
table(df$marital.status)
table(df$occupation)
table(df$relationship)
table(df$race)
table(df$sex)
table(df$native.country)
table(df$income)
```
?, Unknown, Not Known

4. Replace all the forms of missing values found to NA

```{r}
df = df %>% na_if("?") %>% na_if("Unknown") %>% na_if("Not Known")
```

5. Replot the number of NAs for each column. 

```{r}
aggr(df)
```

6. Approach 1 to handle NAs: remove all rows that have any NAs. Save the dataset after removing as a different data. The original data is unchanged (still have NAs).  How many rows left after removing?

```{r}
df2 = drop_na(df)

df2
```
29865 rows left

7. Approach 2 to handle NAs:  Fill all the NAs with the previous or next value. (Hint: Using `fill` function).  Save the dataset after filling as a different data. The original data is unchanged (still have NAs). 

```{r}
df3 = df %>% fill(.direction="updown")
```

8. Approach 3 to handle NAs: For numeric variable, replace the NAs by the median.  For categorical variables, replace the NAs to the majority. 

```{r}
df$age = replace_na(df$age, mean(df$age, na.rm=TRUE))
df$fnlwgt = replace_na(df$fnlwgt, mean(df$fnlwgt, na.rm=TRUE))
df$education.num = replace_na(df$education.num, mean(df$education.num, na.rm=TRUE))
df$capital.gain = replace_na(df$capital.gain, mean(df$capital.gain, na.rm=TRUE))
df$capital.loss = replace_na(df$capital.loss, mean(df$capital.loss, na.rm=TRUE))
df$hours.per.week = replace_na(df$hours.per.week, mean(df$hours.per.week, na.rm=TRUE))

df$workclass = replace_na(df$workclass, names(which.max(table(df$workclass))))
df$education = replace_na(df$education, names(which.max(table(df$education))))
df$marital.status = replace_na(df$marital.status, names(which.max(table(df$marital.status))))
df$occupation = replace_na(df$occupation, names(which.max(table(df$occupation))))
df$relationship = replace_na(df$relationship, names(which.max(table(df$relationship))))
df$race = replace_na(df$race, names(which.max(table(df$race))))
df$sex = replace_na(df$sex, names(which.max(table(df$sex))))
df$native.country = replace_na(df$native.country, names(which.max(table(df$native.country))))
df$income = replace_na(df$income, names(which.max(table(df$income))))

colSums(is.na(df))
```
